Viscous Erosion in Porous Media

### 2018-01-31 docs/methods/erosion_methods.tex
NM

The fixed-area simulations allow us to make precise measurements of the body's opening angle and aspect ratio.

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}[p]%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{./figs/arangle.pdf}
\caption{Aspect ratio and opening angle}
\label{}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024c5
% Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0

>>>>

The fixed-area simulations allow us to make precise measurements of the body's opening angle and aspect ratio as displayed in Fig.~\ref{arangle}. Figure \ref{arangle}a shows the aspect ratio, defined as the body's horizontal compared to its vertical width. The initial circular geometry has an aspect ratio of unity. As erosion causes the body to become more slender, the aspect ratio increases and tends to a value of $2.6$ in long time.

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}[p]%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{./figs/arangle.pdf}
\caption{Aspect ratio and opening angle}
\label{arangle}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024c5
% Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0

@@
